Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-11-14 docs/00-manuscripts/mdpi/tune-perc-sel-features.tex
update tune results table

% latex table generated in R 4.0.4 by xtable 1.8-4 package
\begin{table}[ht!]
\centering
\caption{Selected feature portions during tuning for the best performing learner-filter settings (SVM Relief, RF Relief, XGBoost CMIM) across folds for task HR-NRI-VI, sorted by plot name. 'Features (\texttt{\#})' denotes the absolute number of features selected and 'Features (\texttt{\%})' refers to the percentage relative to the overall features available in the training sets for each plot (Laukiz1 = 1249, Laukiz2 = 1357, Luiando = 1507, Oiartzun = 1311). Results were estimated in a separate model tuning step, not within the main cross-validation comparison.} 
\label{tab:tune-perc-sel-features}
\begin{tabular}{llrl}
  \toprule
Learner & Test Plot & Features (\%) & Features (\#) \\ 
  \midrule
\multirow{4}{*}{\specialcell{RF \\ Relief}} & Laukiz1 & 0.00614 & 1/1249 \\ 
   & Laukiz2 & 16.58887 & 226/1357 \\ 
   & Luiando & 0.06681 & 2/1507 \\ 
   & Oiartzun & 65.06532 & 854/1311 \\ 
  \midrule\multirow{4}{*}{\specialcell{SVM \\ Relief}} & Laukiz1 & 0.50917 & 7/1249 \\ 
   & Laukiz2 & 91.95721 & 1248/1357 \\ 
   & Luiando & 0.50917 & 8/1507 \\ 
   & Oiartzun & 19.70660 & 259/1311 \\ 
  \midrule\multirow{4}{*}{\specialcell{XGB \\ CMIM}} & Laukiz1 & 93.70844 & 1171/1249 \\ 
   & Laukiz2 & 3.51986 & 48/1357 \\ 
   & Luiando & 0.12474 & 2/1507 \\ 
   & Oiartzun & 85.28181 & 1119/1311 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 4.0.4 by xtable 1.8-4 package
\begin{table}[ht!]
\centering
\caption{Selected feature portions during tuning for the best performing learner-filter settings (SVM Relief, RF Relief, XGBoost CMIM) across folds for task HR-NRI-VI, sorted by plot name. 'Features (\texttt{\#})' denotes the absolute number of features selected and 'Features (\texttt{\%})' refers to the percentage relative to the overall features available in the training sets for each plot (Laukiz1 = 1249, Laukiz2 = 1357, Luiando = 1507, Oiartzun = 1311). Results were estimated in a separate model tuning step, not within the main cross-validation comparison.} 
\label{tab:tune-perc-sel-features}
\begin{tabular}{llrl}
  \toprule
Learner & Test Plot & Features (\%) & Features (\#) \\ 
  \midrule
\multirow{4}{*}{\specialcell{RF \\ Car}} & Laukiz1 & 0.00245 & 1/1249 \\ 
   & Laukiz2 & 0.00359 & 1/1357 \\ 
   & Luiando & 0.12448 & 2/1507 \\ 
   & Oiartzun & 2.80356 & 37/1311 \\ 
  \midrule\multirow{4}{*}{\specialcell{SVM \\ Car}} & Laukiz1 & 16.76686 & 210/1249 \\ 
   & Laukiz2 & 40.77700 & 554/1357 \\ 
   & Luiando & 43.80604 & 661/1507 \\ 
   & Oiartzun & 81.23205 & 1065/1311 \\ 
  \midrule\multirow{4}{*}{\specialcell{XGB \\ Borda}} & Laukiz1 & 79.54091 & 994/1249 \\ 
   & Laukiz2 & 0.96545 & 14/1357 \\ 
   & Luiando & 66.27871 & 999/1507 \\ 
   & Oiartzun & 41.89759 & 550/1311 \\ 
   \bottomrule
\end{tabular}
\end{table}
